Towards understanding the central limit theorem by learning Python basics

### 2021-02-17 paper/article.tex
Minor update on the text

The first example is shown in Fig.~\ref{main-py-window}. We kept the original version to highlight
the possibility to write special characters in the Python code (we used Python version 3),
including accented German letters. In the first set of problems each student had to try
the code on his or her own on the website \url{https://repl.it/languages/python3},
by paying attention on the correct indentation as well. We instructed all students with an
explanatory screenshot how the program should be started and the output obtained.

>>>>

The first example is shown in Fig.~\ref{main-py-window}. We kept the original version to highlight
the possibility to write special characters in the Python code (we used Python version 3),
including accented German letters. In the first set of problems each student had to try
the code on his or her own on the website \url{https://repl.it/languages/python3},
by paying attention on the correct indentation as well---the students, however, did not have
to type the code but just copy it from the email into the programming window.
We also instructed all students with an
explanatory screenshot how the program should be started and the output obtained.
